Exploring Disparate Data: Part 1

### 2024-11-04 A3-Pt1.Rmd
Update A3-Pt1.Rmd

---
title: "Exploring Disparate Data: Part 1"
author: "Put your group number from MyLS here: "
date: "Due November 12th"
---

@@

```{r convert_latlon, error=TRUE}
convert_latlon <- function(latlon) {
    # YOUR CODE HERE
}

>>>>

---
title: "Exploring Disparate Data: Part 1"
author: "Put your group number from MyLS here: 8"
date: "Due November 12th"
---

@@

```{r convert_latlon, error=TRUE}
convert_latlon <- function(latlon) {

  parsed_num <- parse_number(latlon)
    if_else(str_detect(latlon, "[SW]"), -parsed_num, parsed_num)
}
